Error Summary (teaching-v2.0)

### 2020-11-16 script/R/preprocessor/error_summary.Rmd
upload summary
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Error Summary (teaching-v1.0)"
output: html_notebook
---

@@

## ONSET
### Corrected Error Onset (All)
```{r onset_all, echo = FALSE}
error_onset_all <- error_onset[CorrectionNr != "Exclude",]
error_onset_all
```

@@

1. **2 participants should be removed from the entire data analysis because they missed at least one block (16 trials)**

- SubNr 3: experimental error (8 trials)
- SubNr 14: played in octave higher (8 trials)

2. **some performances were removed because 1) participants didn't follow sheet music or 2) participants didn't finish till the end (5 trials)**

@@

# separate errors depending on reasons
# SubNr 11, BlockNr 4, TrialNr 8
error_offset_all <- rbind(error_offset_all, error_offset_all[4])
error_offset_all$Reason[4] <- "Extra Notes"
error_offset_all$CorrectionNr[4] <- 1
error_offset_all$Reason[nrow(error_offset_all)] <- "Substituted"
error_offset_all$CorrectionNr[nrow(error_offset_all)] <- 2
# SubNr 27, BlockNr 3, TrialNr 6
error_offset_all <- rbind(error_offset_all, error_offset_all[5])
error_offset_all$Reason[5] <- "Extra Notes"
error_offset_all$CorrectionNr[5] <- 1
error_offset_all$Reason[nrow(error_offset_all)] <- "Substituted"
error_offset_all$CorrectionNr[nrow(error_offset_all)] <- 6

>>>>

---
title: "Error Summary (teaching-v2.0)"
output: html_notebook
---

@@

## ONSET
### Corrected Error Onset (All)
```{r onset_all, echo = FALSE}
error_onset_all <- error_onset[CorrectionNr != "Exclude",]

# separate errors depending on reasons
# SubNr 10, BlockNr 1, TrialNr 6
error_onset_all <- rbind(error_onset_all, error_onset_all[2])
error_onset_all$Reason[2] <- "Extra Notes"
error_onset_all$CorrectionNr[2] <- 2
error_onset_all$Reason[nrow(error_onset_all)] <- "Substituted"
error_onset_all$CorrectionNr[nrow(error_onset_all)] <- 1

error_onset_all
```

@@

@@

# separate errors depending on reasons
# SubNr 1, BlockNr 2, TrialNr 3
error_offset_all <- rbind(error_offset_all, error_offset_all[1])
error_offset_all$Reason[1] <- "Extra Notes"
error_offset_all$CorrectionNr[1] <- 1
error_offset_all$Reason[nrow(error_offset_all)] <- "Substituted"
error_offset_all$CorrectionNr[nrow(error_offset_all)] <- 4
# SubNr 8, BlockNr 4, TrialNr 2
error_offset_all <- rbind(error_offset_all, error_offset_all[5])
error_offset_all$Reason[5] <- "Extra Notes"
error_offset_all$CorrectionNr[5] <- 1
error_offset_all$Reason[nrow(error_offset_all)] <- "Substituted"
error_offset_all$CorrectionNr[nrow(error_offset_all)] <- 2
# SubNr 10, BlockNr 1, TrialNr 6
error_offset_all <- rbind(error_offset_all, error_offset_all[6])
error_offset_all$Reason[6] <- "Extra Notes"
error_offset_all$CorrectionNr[6] <- 2
error_offset_all$Reason[nrow(error_offset_all)] <- "Substituted"
error_offset_all$CorrectionNr[nrow(error_offset_all)] <- 1
# SubNr 15, BlockNr 3, TrialNr 5
error_offset_all <- rbind(error_offset_all, error_offset_all[7])
error_offset_all$Reason[7] <- "Extra Notes"
error_offset_all$CorrectionNr[7] <- 1
error_offset_all$Reason[nrow(error_offset_all)] <- "Substituted"
error_offset_all$CorrectionNr[nrow(error_offset_all)] <- 2
